---
title: "Lancet Paper supplementary material"
output: 
  bookdown::html_document2:
    toc: yes
    toc_depth: 4
    toc_float: yes
    number_sections: no
    theme: flatly
    highlight: kate 
    fig.caption: yes 
    tables: true 
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
  fig.align = "center",
  fig.width = 12,
  fig.height = 8
)
```

```{css, echo = F}
<!-- .header1 { -->
<!-- color: #8a2587; -->
<!-- } -->

.caption {
margin: auto;
text-align: left;
}
```

```{r, warning = F, message = F, include = F, echo = F}
myColour <- "#8a2587"
```

# Introduction

The supplementary material for the lancet paper looking at how different service components effect key clinical outcomes and health care use. This additional material demonstrates on a set of synthetic data, the data processing and analysis carried out for the paper "X". 

# Library 

These are the packages that were used in the analysis of the data. Please note, the version numbers might be different, but the methods are still the same. 

```{r load libraries, warning = F, message = F}
# packages for analysis and processing
library(tidyverse)
library(tidybayes)
library(brms)
library(lubridate)

# packages for figures and tables in this document 
library(see)
library(ggridges)
```

```{r figure settings, echo = F}
# Sort out the theme
textSize <- 17:20
theme_set(theme_bw())
theme_update(
  title = element_text(size = textSize[3]),
  axis.text = element_text(size = textSize[2]),
  axis.title = element_text(size = textSize[3]),
  legend.text = element_text(size = textSize[1])
)
```





